### 2017-02-26 2017mergingmerges/section/03-Definition.tex
Shift Action grammar to process def fig
Only talk about single process evaluation in 'Shaking'

% -----------------------------------------------------------------------------
\eject{}
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. The judgment form $\ProcInject{p}{v}{c}{p'}$ reads ``given process $p$, injecting value $v$ into channel $c$ yields a new process $p'$''. The @injects@ form is similar, but operates on sets of processes rather than a single one.

@@

% -----------------------------------------------------------------------------
\subsubsection{Shaking}
Fig.~\ref{fig:Process:Eval:Shake} defines the judgment forms and rules for shaking a process, allowing it to take a step, and produce an output message.
% I don't like them, but alpha and tau are standard names in process calculi. 
The type of messages is denoted by $\alpha$, which can either be ($\Push~\Chan~\Value$) for pushing a value to a particular channel, or $\tau$ for an `internal' message which only performs local state updates.

The judgment form for shaking a single instruction $\ProcBlockShake{x}{i}{\Sigma}{\alpha}{l'}{i'}{u'}$
executes an instruction $x$ with the input states $i$ and the heap $\Sigma$.
The result contains an output message $\alpha$, as well as the new label $l'$, the new input state $i'$, and the update substitution to apply to the heap $u'$.

Rule (Pull) takes an already injected value from the input buffer, which changes its state from @pending@ to @have@.
The result substitution sets the variable to the pulled value, as well as any substitutions in the \Next~ of the instruction.

>>>>

% -----------------------------------------------------------------------------
\eject{}
\subsubsection{Injection}
Fig.~\ref{fig:Process:Eval:Inject} gives the rules for injecting values into processes. A judgment of form $(\ProcInject{p}{v}{c}{p'})$ reads ``given process $p$, injecting value $v$ into channel $c$ yields a new process $p'$''. The @injects@ form is similar, but operates on sets of processes rather than a single one.

@@

% -----------------------------------------------------------------------------
\subsubsection{Shaking}
Fig.~\ref{fig:Process:Eval:Shake} gives the rules for advancing a single process. The first set of rules handle specific instructions. A judgment of form $(\ProcBlockShake{i}{is}{\Sigma}{\alpha}{l}{is'}{us})$ reads ``instruction $i$, given channel states $is$ and the heap $\Sigma$, passes control to instruction at label $l$ and yields new channel states $is$, heap update expressions $us'$, and performs action $\alpha$.'' An action $\alpha$ is a list of messages of the form $(\Push~\Chan~\Value)$, which encode the values a process pushes to its output channels. We write ~$\cdot$~ for an empty action.

% The type of messages is denoted by $\alpha$, which can either be ($\Push~\Chan~\Value$) for pushing a value to a particular channel, or $\tau$ for an `internal' message which only performs local state updates.

% The judgment form for shaking a single instruction $\ProcBlockShake{x}{i}{\Sigma}{\alpha}{l'}{i'}{u'}$ executes an instruction $x$ with the input states $i$ and the heap $\Sigma$. The result contains an output message $\alpha$, as well as the new label $l'$, the new input state $i'$, and the update substitution to apply to the heap $u'$.

\eject{}
Rule (Pull) takes an already injected value from the input buffer, which changes its state from @pending@ to @have@.
The result substitution sets the variable to the pulled value, as well as any substitutions in the \Next~ of the instruction.
